Code Publishing Tutorial

### 2024-11-26 index.qmd
Remove Manubot as it's not primarily for executing code

>>>>

::: {#nte-quarto-alternatives .callout-note collapse="true"}
## Alternatives to Quarto

Quarto is a tool to create reproducible documents, but not the only one. You may also use [RMarkdown](https://rmarkdown.rstudio.com/), [Jupyter Book](https://jupyterbook.org/), [Stencila](https://stencila.io/), [Curvenote](https://curvenote.dev/), [showyourwork!](https://show-your.work/), or one of the countless others.
:::
